Turbulence in compact to giant HII regions

### 2021-09-03 mnras_template.tex
Javier changes to Aug 20
Javier changes up to 2021-09-03

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. García-Vázquez et al.]{
J. García Vázquez,$^{1}$\thanks{E-mail: jgarciav1600@alumno.ipn.mx}
J. Zsargo,$^{1}$
W. J. Henney$^{2}$
and H. O. Castañeda$^{1}$
\\
% List of institutions
$^{1}$Escuela Superior de Física y Matemáticas, Instituto Politécnico Nacional, Ciudad de México, México.\\
$^{2}$Instituto de Radioastronomía y Astrofísica, Universidad Nacional Autonoma de México, Apartado postal 3-72, 58090 Morelia, Michoacán, Mexico\\
}

@@

% Abstract of the paper
\begin{abstract}
  Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
  We apply the technique to archival \halpha\ observations of a diverse sample of 9 \hii{} regions
  in the Milky Way and other Local Group galaxies,
  which span more than two orders of magnitude in size and luminosity.
  By fitting a simple functional form to the second-order velocity structure function,
  we extract three parameters for the fluctuations in each region:
  total velocity dispersion, \(\sigma\),
  autocorrelation length, \(r_0\), and power-law slope, \(m\).
  The velocity dispersion is found to correlate primarily with luminosity,
  while the autocorrelation length correlates primarily with the size of the region.
  The power-law slope shows an apparent correlation with distance,
  but this is probably an artifact of poor spatial resolution for the most distant regions.
  \textbf{Add a sentence about the conclusions!}
  % We study the turbulent velocity fluctuations in the ionized gas of four giant HII regions using the radial velocity field in the H$\alpha$ emission line. The data was acquired by long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope. Each velocity sample is statistically analyzed with the second order structure function. The correlations in our results shows evidence that the velocity field can be consider in a turbulent state. This turbulent motions are described by a power-law with a mean index of 1.7 for different sized regions at different distances. The physical interpretation of the power-law behavior consider that an energy cascade is taking place in the photoionized gas.
\end{abstract}

@@

\definecolor{WillCommentColor}{rgb}{0.6,0.11,0.4}
\newcommand\WILL[1]{\textbf{\color{WillCommentColor}#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Introduction}
\WILL{I think it would be best to lead with a description of the dynamics of H II regions before mentioning the turbulence}.

It is known that the speed of sound in a HII region is of the order of \(c_{HII} \sim\) 13 km s\kms.
\citet{smith1970} discovered that the probable velocities of internal motions of extragalactic HII regions, \(\sigma_{W}\) (line width integrated over the whole HII region), were in the range of $\sim$ 19-34 km s\kms\ covering supersonic values.
\citet{skillman1984kinematics} found broad profiles in giant extragalactic HII regions (GEHRs) that have a FWHM\(>\)30km s\kms. 
This property is mainly used to distinguish between 'normal' and 'giant' HII regions. Other differences are their size, luminosity and their stellar population. 
For the velocity to be supersonic it is necessary a continuous mechanism to maintain the observed motions, as supersonic motions are expected to dissipate energy via shocks \citep{1994Ap&SS.216..285C}.
Also, this non-thermal broadening on the spectral emission lines has been suggested as evidence of disorder motions along the line-of-sight (LOS) of the ionized gas. 
Turbulence is suggested as a mechanism that can stir the medium and maintain the supersonic velocities.

The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are the main properties that supports the idea of a turbulent interstellar medium.
Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field that can be interpreted as evidence of random motions.

The usual picture considers that interstellar turbulence is driven on different scales by various energetic processes.
Also, it is thought that the formation of structures like filaments and shells in the diffuse medium is determined by large-scale turbulence.
Stars are the mainly mechanism proposed to account for the large input of kinetic energy through UV radiation, but the dominant energetic sources and their relation to turbulence still is unclear.

@@

The paper follows the next order...
Section 2...

\section{HII regions sample}

We used previous published observational data to measure the second-order velocity structure function for a number of compact and lower luminosity regions. Table \ref{tab:Reg} shows the HII regions names
with physical properties of each region.

\subsection{Regions in the Milky Way and Large Magellanic Cloud}
\label{sec:regions-milky-way}

We use data from \citet{1987A&A...176..347H} of the Orion Nebula (M42) located at 440 pc \citep{2008AJ....136.1566O}.
Its physical and kinematics properties along its stellar population are well documented in the review of \citet{2001ARA&A..39...99O}.
The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) with fast stellar wind, and 3 B-type stars from the Trapezium cluster.
The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region \citep{arthur2016turbulence}.

A 106 cm-Cassegrain telescope at Observatorium Hoher List was used with a Fabry-Pérot interferometer having the étalon a separation of 0.5 mm. 
Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
The exposures are overlapped and fall into one square of a grid with a width of 1' sentered at \(\theta^{1}\)Ori C \citep{1987A&A...176..347H}.

The Carina Nebula is located at a distance of 2.35$\pm$0.05 kpc \citep{2006ApJ...644.1151S}.
Young clusters like Trumpler 14 and 16, and Collinder 228 together they form the Car OB1 association.
This OB association has more than 60 stars earlier than B0, and several Wolf-Rayet stars.
The most star is a luminous blue variable, $\eta$ Car \citep{Damiani:2016a}.

The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citep{2005A&A...430..941P}.
It is present on the nebula the young stellar cluster NGC6530.
The region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the star Herschel 36, type O7 \citep{1986AJ.....91..870W}.

@@

Using observations observations from \citet{Castro:2018a} (private communication) we study the Tarantula Nebula (30~Dor) in the LMC.
At a distance of 49.9 kpc \citep{2013Natur.495...76P} is the most luminous star-forming complex in the Local Group \citep{1984ApJ...287..116K}.
The star forming region NGC 2070 host the massive star cluster R136.

NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very LArge Telescope (VLT). 
Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed. 
The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalogue of \citet{1999A&A...341...98S}. 
The final spectra span 495-9366 A, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Application to our HII regions sample}

@@

The Table \ref{tab:Data} shows the statistical properties of each individual sample.
The mean, \(\mu\), and the variance, \(\sigma^{2}\), along the number of points of each sample.
The last column shows previous publications where the data was used. 
For the first 4 regions in Table \ref{tab:Data} the value of \(\mu\) is the observed radial velocity accounting for heliocentric correction and subtracting the corrected radial velocity value of the most luminous pixel.

%In appendix \ref{sec:VelMaps} we show in the Figure \ref{fig:hist} the histograms of the velocity samples of each HII region where we applied equation \ref{eq:S}.
%The Figures \ref{fig:M604}-\ref{fig:MOrion} show the two-dimensional radial velocity map of each region.

\begin{table*}
  \begin{center}
    \caption{General statistical properties of the centroid velocities.
      a) \citet{tanco1997}
      b) \citet{2019arXiv191203543M}
      c) \citet{Castro:2018a}
      d) \citet{Damiani:2016a}
      e) \citet{Damiani:2017b}
      f) \citet{1987A&A...176..347H}
      g) \citet{arthur2016turbulence}.
    } 
\begin{tabular}{cccccc}\hline
HII         &$\mu$   &$\sigma^{2}$       &No. of  &\(s_0\)* & Previously \\
Region      &[km/s]  &[km$^{2}$/s$^{2}$] &points  &[pc]     & used in:   \\ \hline
NGC 604     &3.56    &54.63              &9 510   &1.73     &a,b         \\
NGC 595     &2.82    &44.13              &8 765   &1.73     &-           \\
Hubble V    &-1.23   &7.87               &5 832   &1.02     &-           \\
Hubble X    &-5.95   &12.9               &6 925   &1.02     &-           \\
30Dor       &265.56* &252.79             &363 059 &0.2      &c           \\
Carina      &-8.83   &17.89              &855     &         &d           \\
NGC 346     &        &31.36              &112 796 &         &            \\
Lagoon      &-6.26   &7.53               &1 176   &         &e           \\
Orion Large &-1.25   &10.43              &359     &         &f           \\
Orion Small &        &9.61               &        &         &g            \\ \hline
\end{tabular}\label{tab:Data}
\end{center}
\end{table*}

@@

\begin{table*}
\begin{center}\caption{Main results.}
\begin{tabular}{ccccccccc}\hline
HII         &\(\sigma\) &\(r_0\)                     &\(m\)   &Reduced &\(\langle \sigma_{LOS} \rangle \) \\
Region      &[km/s]     &[pc]                        &                           &chi-square &  [km/s]\\ \hline
NGC 604     &7.39       &8.75\(^{+0.68}_{-0.75}\)    &1.95\(^{+0.12}_{-0.14}\)   &0.81 &16.2  \\
NGC 595     &6.64       &8.99\(^{+0.58}_{-0.71}\)    &1.75\(^{+0.10}_{-0.10}\)   &0.47 &18.3  \\
Hubble V    &2.80       &2.7\(^{+0.24}_{-0.14}\)     &1.62\(^{+0.11}_{-0.09}\)   &0.19 &13.4  \\ 
Hubble X    &3.59       &3.62\(^{+0.18}_{-0.15}\)    &1.7\(^{+0.08}_{-0.09}\)    &0.13 &12.3  \\   
30 Dor      &15.8       &2.69\(^{+0.08}_{-0.03}\)    &1.22\(^{+0.022}_{-0.007}\) &0.49 &31.7* \\
Carina      &4.22       &0.94\(^{+0.94}_{-0.13}\)    &0.82\(^{+0.08}_{ -0.08}\)  &0.39 &22.4   \\
NGC 346     & 5.6       &1.4\(^{+0.05}_{-0.75}\)     &1.13\(^{+0.03}_{-0.03}\)   &0.34 &  \\
Lagoon      &2.7        &1.78\(^{+0.07}_{-0.07}\)    &1.56\(^{+0.05}_{-0.05}\)   &0.59 &13.6     \\ 
Orion Large &3.23       &0.84\(^{+0.37}_{-0.24}\)    &0.9\(^{+0.04}_{-0.04}\)    &0.27 &6  \\
Orion Small &3.1        & 0.062\(^{+0.003}_{-0.001}\)&1.44\(^{+0.11}_{-0.01}\)   &0.64 &6 \\\hline	  
\end{tabular}\label{tab:Res}
\end{center}
\end{table*}

%\begin{table*}
%\begin{center}\caption{Main results.}
%\begin{tabular}{ccccccccccc}\hline
%HII    &  \(\sigma\) &   \(r_0\) &    \(m\)   &Reduced& r$_{2\sigma}$* &  \(r_{max}\)/\(r_0\)* & \(\langle \sigma_{LOS} \rangle \) & \(l_T\)* & \(Re\)*& - \\
%Region    &  [km/s] &  [pc]    &&   chi-square     & [pc] &      &[km/s]& [pc] & &  \\ \hline
%NGC 604   &  7.39   &  8.75\(^{+0.68}_{-0.75}\)    &   1.95\(^{+0.12}_{-0.14}\)  &0.81& 27   & 14.7 & 16.2 &  5.1 & &  \\
%NGC 595   &  6.64   &  8.99\(^{+0.58}_{-0.71}\)    &   1.75\(^{+0.10}_{-0.10}\) &0.47& 20   & 21.4 & 18.3 & 4.4  & &  \\
%Hubble V  &  2.80   &  2.7\(^{+0.24}_{-0.14}\)   &   1.62\(^{+0.11}_{-0.09}\)  & 0.19& 12   & 19.9 &  13.4    & 1.56 & &  \\ 
%Hubble X  &  3.59   &  3.62\(^{+0.18}_{-0.15}\)    &   1.7\(^{+0.08}_{-0.09}\) &0.13& 15   & 22.1 &  12.3    & 1.95 & &  \\   
%30 Dor    &  15.8    &   2.69\(^{+0.08}_{-0.03}\)    &   1.22\(^{+0.022}_{-0.007}\) &0.49& 11   & 8.9  &      & 0.69 & &  \\
%Carina    &  4.22    &    0.94\(^{+0.94}_{-0.13}\)     &    0.82\(^{+0.08}_{ -0.08}\)   &0.39& 2    & 16.1 & 22.4  &      & &  \\
%NGC 346   &   5.6    &  1.4\(^{+0.05}_{-0.75}\)     &    1.13\(^{+0.03}_{-0.03}\) &0.34&     &     &     &  & &  \\
%Lagoon    &  2.7     &   1.78\(^{+0.07}_{-0.07}\)     &   1.56\(^{+0.05}_{-0.05}\) &0.59&  6   & 10.1 &  13.6    &      & &  \\ 
%Orion Large &  3.23    &   0.84\(^{+0.37}_{-0.24}\)    &   0.9\(^{+0.04}_{-0.04}\) &0.27&  -   & 27.6 &   6  &      & &  \\
%Orion Small &   3.1 & 0.062\(^{+0.003}_{-0.001}\)      &  1.44\(^{+0.11}_{-0.01}\)  &0.64&     &  &  6   &      &  & \\	  
%\end{tabular}\label{tab:Res}
%\end{center}
%\end{table*}

%\subsection{Plane of sky radial velocity dispersion \(\sigma\)}

@@

@@

\subsection{Other significant scales}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. García Vázquez et al.]{
J. García Vázquez,$^{1}$\thanks{E-mail: jgarciav1600@alumno.ipn.mx}
J. Zsargo,$^{1}$
W. J. Henney$^{2}$
and H. O. Castañeda$^{1}$
\\
% List of institutions
$^{1}$Escuela Superior de Física y Matemáticas, Instituto Politécnico Nacional, Ciudad de México, México.\\
$^{2}$Instituto de Radioastronomía y Astrofísica, Universidad Nacional Autonoma de México, Apartado postal 3-72, 58090 Morelia, Michoacán, Mexico\\
}

@@

% Abstract of the paper
\begin{abstract}
  Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
  To characterize these fluctuations we apply a statistical analysis using the second-order structure function to archival \halpha\ observations of a diverse sample of 9 \hii{} regions.
  This regions are located in the Milky Way and other Local Group galaxies, and
  span more than two orders of magnitude in size and luminosity.
  By fitting a simple functional form of the structure function to our results
  we extract three parameters related to the fluctuations in each region: the
  total velocity dispersion \(\sigma\), which spans from 3 to 15 km s\(^{-1}\), the
  autocorrelation length \(r_0\), which covers 0.06 - 8 pc, and the power-law slope \(m\), which ranges from 0.82 to 1.95.
  The velocity dispersion is found to correlate primarily with luminosity,
  while the autocorrelation length correlates primarily with the size of the region.
  The power-law slope shows an apparent correlation with distance,
  but this is probably an artifact of poor spatial resolution for the most distant regions.
  A comparison between \(\sigma\) and \(\sigma_{POS}\) shows that this last value is at roughly the double for all regions.
  \textbf{Add a sentence about the conclusions!}
  % We study the turbulent velocity fluctuations in the ionized gas of four giant HII regions using the radial velocity field in the H$\alpha$ emission line. The data was acquired by long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope. Each velocity sample is statistically analyzed with the second order structure function. The correlations in our results shows evidence that the velocity field can be consider in a turbulent state. This turbulent motions are described by a power-law with a mean index of 1.7 for different sized regions at different distances. The physical interpretation of the power-law behavior consider that an energy cascade is taking place in the photoionized gas.
\end{abstract}

@@

@@

\section{Introduction}

It is known that the speed of sound in a HII region is of the order of \(c_{HII} \sim\) 13 km s\kms.
\citet{smith1970} discovered that the probable velocities of internal motions of extragalactic HII regions, \(\sigma_{W}\) (line width integrated over the whole HII region), were in the range of $\sim$ 19-34 km s\kms\ covering supersonic values.
\citet{skillman1984kinematics} found broad profiles in giant extragalactic HII regions (GEHRs) that have a FWHM\(>\)30km s\kms. 
This property is mainly used to distinguish between 'normal' and 'giant' HII regions. Other differences are their size, luminosity and their stellar population. 
For the velocity to be supersonic it is necessary a continuous mechanism to maintain the observed motions, as supersonic motions are expected to dissipate energy via shocks \citep{1994Ap&SS.216..285C}.
Also, this non-thermal broadening on the spectral emission lines has been suggested as evidence of disorder motions along the line-of-sight (LOS) of the ionized gas. 
Turbulence is suggested as a mechanism that can stir the medium and maintain the supersonic velocities. 
The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are the main properties that supports the idea of a turbulent interstellar medium.
Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field that can be interpreted as evidence of random motions.
The usual picture considers that interstellar turbulence is driven on different scales by various energetic processes.
Also, it is thought that the formation of structures like filaments and shells in the diffuse medium is determined by large-scale turbulence.
Stars are the mainly mechanism proposed to account for the large input of kinetic energy through UV radiation, but the dominant energetic sources and their relation to turbulence still is unclear.

@@

The paper follows the next order: in Section \ref{sec:HIIsample} we describe the observational data and some main kinematics properties of each region. In Section \ref{sec:met} we present the statistical method used in this work. Section \ref{sec:results} presents the structure function of each region along with the turbulent parameters obtained by a non-linear regression method. In Section \ref{sec:discussion} we discuss our findings in the context of previous works.

\section{HII regions sample}\label{sec:HIIsample}

We use previous published observational data to measure the second-order velocity structure function for a number of nine HII regions. 
Table \ref{tab:Reg} shows the HII regions names
with the main physical properties of each region. 
These regions are located in the Milky Way, the Magellanic clouds and in the M 33 and NGC 6822 galaxies.

\subsection{Regions in the Milky Way and Magellanic Clouds}
\label{sec:regions-milky-way}

Orion is a galactic HII region located at a distance of 440 pc \citep{2008AJ....136.1566O}.
The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) with fast stellar wind, and 3 B-type stars from the Trapezium cluster.
The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region \citep{arthur2016turbulence}.
Its physical and kinematics properties along its stellar population are well documented in the review of \citet{2001ARA&A..39...99O}.

We use data from \citet{1987A&A...176..347H} and \citep{arthur2016turbulence} to study of turbulence in the Orion Nebula.
\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
A Fabry-Pérot interferometer was used having the étalon a separation of 0.5 mm. 
Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.

\citet{arthur2016turbulence} observations were initially published by \citet{2008RMxAA..44..181G}. The data were obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory. These observation cover 3 \(\times\) 5 arcmin\(^{2}\)of the Orion nebula and the data consist of 96, 300 arcsec North-South orientated slits at 2 arcsec intervals with a width of 0.8 arcsec. The velocity resolution is 8 km s\(^{-1}\).

The Carina nebula is located at a distance of 2.35$\pm$0.05 kpc \citep{2006ApJ...644.1151S}.
Young clusters like Trumpler 14 and 16, and Collinder 228 together form the Car OB1 association.
This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet stars.
The most star is a luminous blue variable, $\eta$ Car \citep{Damiani:2016a}.
The stellar content has lead to identify the Carina nebula as a star formation region, and as such it presents several phenomena related with young stras as (\citet{2006ApJ...644.1151S} and reference therein): evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars, Herbig-Haro objects, to mention some. 
All of these phenomena are consequence of the UV radiation and stellar winds from star clusters in the HII region.

The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citep{2005A&A...430..941P} and contains the young stellar cluster NGC6530.
The region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the star Herschel 36, type O7 \citep{1986AJ.....91..870W}. 
The velocity field shows several expanding shells, related to the cluster NGC 6530, the O stars 9 Sgr and Herschel 36, and the massive protostar M8East-IR. A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}.

@@

Using observations from \citet{Castro:2018a} (private communication) we study the Tarantula Nebula (30 Doradus).
This nebula us located in the LMC (Large Magellanic Cloud) at a distance of 49.9 kpc \citep{2013Natur.495...76P} and is the most luminous star-forming complex in the Local Group \citep{1984ApJ...287..116K}.
It host the star forming region NGC 2070 that contains the massive star cluster R136.
NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very Large Telescope (VLT). 
Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed. 
The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalogue of \citet{1999A&A...341...98S}. 
The final spectra span 495-9366 A, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.

NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 60 kpc. 
It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
\citet{2008ApJ...688.1050G} propose an expanding H II region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region in addition to the photoionizing process of the OB stars. 
This mechanism is similar to shell-like H ii regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Application to our HII regions sample}\label{sec:apply}

@@

The Figure \ref{fig:hist} shows the histograms of each individual sample with the variance  \(\sigma^{2}\), along the number of points of each sample.

%\begin{table*}
%  \begin{center}
%    \caption{General statistical properties of the centroid velocities.} 
%\begin{tabular}{cccc}\hline
%HII         &$\mu$   &$\sigma^{2}$       &No. of  \\
%Region      &[km/s]  &[km$^{2}$/s$^{2}$] &points  \\ \hline
%NGC 604     &3.56    &54.63              &9 510    \\
%NGC 595     &2.82    &44.13              &8 765    \\
%Hubble V    &-1.23   &7.87               &5 832   \\
%Hubble X    &-5.95   &12.9               &6 925   \\
%30Dor       &265.56* &252.79             &363 059 \\
%Carina      &-8.83   &17.89              &855     \\
%NGC 346     &        &31.36              &112 796 \\
%Lagoon      &-6.26   &7.53               &1 176   \\
%Orion Large &-1.25   &10.43              &359     \\
%Orion Small &        &9.61               &        \\ \hline
%\end{tabular}\label{tab:Data}
%\end{center}
%\end{table*}

\begin{figure*}
\centering
\begin{multicols}{3}
\includegraphics[width=1.5in]{Figures/Hist/604}\par
\includegraphics[width=1.5in]{Figures/Hist/595}\par
\includegraphics[width=1.5in]{Figures/Hist/346}\par
\end{multicols}
\begin{multicols}{3}
\includegraphics[width=1.5in]{Figures/Hist/Hubble V}\par
\includegraphics[width=1.5in]{Figures/Hist/Hubble X}\par
\includegraphics[width=1.5in]{Figures/Hist/30Dor}\par
\end{multicols}
\begin{multicols}{3}
\includegraphics[width=1.5in]{Figures/Hist/M8}\par
\includegraphics[width=1.5in]{Figures/Hist/Car}\par
\includegraphics[width=1.5in]{Figures/Hist/OrionS}\par
\end{multicols}
\caption{Histograms of the centroid velocities of our sample of HII regions. }
\label{fig:hist}
\end{figure*}

\subsection{HII regions structure functions}

@@

@@

\begin{figure*}
\centering
\begin{multicols}{3}
\includegraphics[width=2in]{Figures/SFplots/604.pdf}\par
\includegraphics[width=2in]{Figures/SFplots/595.pdf}\par
\includegraphics[width=2in]{Figures/SFplots/346.pdf}\par
\end{multicols}
\begin{multicols}{3}
\includegraphics[width=2in]{Figures/SFplots/Hubble V.pdf}\par
\includegraphics[width=2in]{Figures/SFplots/Hubble X.pdf}\par
\includegraphics[width=2in]{Figures/SFplots/tarantula.pdf}\par
\end{multicols}
\begin{multicols}{3}
\includegraphics[width=2in]{Figures/SFplots/Carina.pdf}\par
\includegraphics[width=2in]{Figures/SFplots/M8.pdf}\par
\includegraphics[width=2in]{Figures/SFplots/OS.pdf}\par
\end{multicols}
\caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line investigated in this work. The first two rows consider extragalactic regions while the last row shows galactic regions.}
\label{fig:SFs}
\end{figure*}

\begin{table*}
\begin{center}\caption{Main results.
 a) \citet{tanco1997}
      b) \citet{2019arXiv191203543M}
      c) \citet{Castro:2018a}
      d) \citet{Damiani:2016a}
      e) \citet{Damiani:2017b}
      f) \citet{1987A&A...176..347H}
      g) \citet{arthur2016turbulence}.}
\begin{tabular}{ccccccccc}\hline
HII         &\(\sigma\) &\(r_0\)                     &\(m\)    &\(\langle \sigma_{LOS} \rangle \) & Previously\\
Region      &[km/s]     &[pc]                        &                           &  [km/s]& used in:\\ \hline
NGC 604     &7.39       &8.75\(^{+0.68}_{-0.75}\)    &1.95\(^{+0.12}_{-0.14}\)   &16.2  &a,b \\
NGC 595     &6.64       &8.99\(^{+0.58}_{-0.71}\)    &1.75\(^{+0.10}_{-0.10}\)   &18.3  &- \\
Hubble V    &2.80       &2.7\(^{+0.24}_{-0.14}\)     &1.62\(^{+0.11}_{-0.09}\)   &13.4  &- \\ 
Hubble X    &3.59       &3.62\(^{+0.18}_{-0.15}\)    &1.7\(^{+0.08}_{-0.09}\)    &12.3  &- \\   
30 Dor      &15.8       &2.69\(^{+0.08}_{-0.03}\)    &1.22\(^{+0.022}_{-0.007}\) &31.7* &c\\
Carina      &4.22       &0.53\(^{+0.12}_{-0.11}\)    &1.19\(^{+0.20}_{ -0.16}\)  &22.4  &d\\
NGC 346     & 5.6       &1.4\(^{+0.05}_{-0.75}\)     &1.13\(^{+0.03}_{-0.03}\)   &10.2* &-\\
Lagoon      &2.7        &1.78\(^{+0.07}_{-0.07}\)    &1.56\(^{+0.05}_{-0.05}\)   &13.6  &e\\ 
Orion Large &3.23       &0.84\(^{+0.37}_{-0.24}\)    &0.9\(^{+0.04}_{-0.04}\)    &6     &f \\
Orion Small &3.1        & 0.062\(^{+0.003}_{-0.001}\)&1.44\(^{+0.11}_{-0.01}\)   &6     &g \\\hline	  
\end{tabular}\label{tab:Res}
\end{center}
\end{table*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Section \ref{sec:apply} we mentioned the reduced chi-square method we are using for determining the correlation length and the index of the slope. Since this is the first time this method is applied to a sample of HII regions (at least for our knowledge), the results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{2019arXiv191203543M}. We will focus on the interpretation of each investigation results and leave the comparison of values as second issue.

A complete analysis on different emissions lines of the structure function on Orion was carried out by \citet{arthur2016turbulence} and reference therein. 
They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
This results just consider one component on the Gaussian fit. 
The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
The correlation length for all lines is \(\approx\) 0.05 pc. For the same \halpha\ observation we obtained a value of 1.44 and a correlation length of 0.062 pc. 
As a comparison for the large scales \citep{1987A&A...176..347H} the value is 0.9 with a considerable agreement with previous results. 
The change in the index could be attributed to the multiple scales of energy injection that are present in the nebula.

The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Doradus complex in the LMC, finding no indication of turbulent motions between scale of 10 and 100 pc.
\citet{2019arXiv191203543M} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula; their observations cover a region where the large-scale velocity fluctuations are uncorrelated.
There is a good agreement with the single-Gaussian fit results from \citet{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results do not overlap with ours.
From the previous this is the first time turbulence structure is found in 30 Doradus through the structure function.

There is broad agreement in our results and previous studies considering NGC 604 from \citet{tanco1997} and \citet{2019arXiv191203543M}, and using the same TAURUS-II data.
Despite this general agreement the interpretations in each study is different.
\citet{tanco1997} conclude about a double regime acting on the kinetic energy spectrum.
According to this double cascading, turbulence is being forced at scales of \(\approx\)10 pc while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\)70 pc.
Interesting enough, \citet{tanco1997} mentioned various characteristic scale lengths, the most notorious is the \(\approx\)10 pc, a value close to our correlation length of \(\approx\)9 pc, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.  
None of the previous studies present a power-law index for the structure function to compare our results.
\citet{2019arXiv191203543M} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
As we agree with them in the importance of observing NGC 604 at higher spatial resolution, we have prove that a consistent method in analyzing structure function is key to obtaining trustworthy results.

For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function between our results and previous investigations.
Our observations cover the brightest part of the region and have smaller resolution.
\citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
\citet{lagrois2011} used the data from \citet{lagrois2009multi} to complement the structure function analysis with the auto correlation function and filters to the velocity field to get rid of non-turbulent movements.
Their sigma is 5.92$\pm$0.15 km/s with a correlation length is 43 pc.
The high difference is because the consider that this happen at 2$\sigma$ (equation 13 on their paper).
The power-law index they provide is 1.55$\pm$0.01.

\subsection{Correlations between physical properties and turbulent parameters}

Using the first three columns in Tables \ref{tab:Reg} and \ref{tab:Res}, we obtain the Pearson correlation coefficient $r$. Between luminosity (L) and \(\sigma\) it is 0.71, between distance (D) and \(m\) the value is 0.73, and finally between size (R) and \(r_0\) we have 0.96. 
By means of a significance test and assuming that a uncorrelated sample produces our results, for the first two relationships we have a probability value $p$ of 0.02 and for the remaining one of <10\(^{-5}\).
Applying and ordinary least-square regression (OLS) we find a form Y = aX + b; this values along the previous ones is shown in Table \ref{tab:RestStats}.
